Choosing climate forcing for numerical simulations of the Cordilleran ice sheet

### 2013-02-18 sections/model.tex
Added section 3 Model setup foreword

%The simulations were run with PISM, a parallel ice sheet model (version stable 0.5.11). Documentation on the code can be found in several publications \citep[e.g.,][]{bueler-brown-2009,aschwanden-etal-2012} and more extensively online \citep[{\url{http://www.pism-docs.org}},][]{web:pism}.

@@

The glacier bed topography response to the ice load is computed by a regional isostasy model with flexure and relaxation \citep{lingle-clark-1985}. To compute basal temperatures with higher accuracy, the thermal model is extended 1\,km into the bedrock. An homogeneous geothermal heat flux of 70\,\unit{W\,m^{-2}} is provided as basal condition to this model.

>>>>

We use PISM, a parallel ice sheet model (version stable 0.5.11). Documentation on the code can be found in several publications \citep[e.g.,][]{bueler-brown-2009,aschwanden-etal-2012} and more extensively online \citep[{\url{http://www.pism-docs.org}},][]{web:pism}.

@@

The glacier bed topography response to the ice load is computed by a regional isostasy model with flexure and relaxation \citep{lingle-clark-1985}\todo{check ref.}. To compute basal temperatures with higher accuracy, the thermal model is extended 1\,km into the bedrock. An homogeneous geothermal heat flux of 70\,\unit{W\,m^{-2}} is provided as basal condition to this model.
